ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467. Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura Gati).}

### 2018-06-15 Latex/Draft_Summer2018/Summer2018.tex
Writing + function to find SS numerically (find_SS_numerically.m)

In order to formally explain which mechanism links current ICT to future TFP, we analyze a 2-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy. Both sectoral production functions are fed with three inputs: (i) labor, supplied by households, (ii) hard capital, produced by the final sector, and (iii) ICT capital, produced by the ICT sector. Along with \cite{basu2007information}, we interpret the nature of ICT as a GPT in a neoclassical essence since we assume exogenous technological changes in the ICT sector. When an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy. We then assume that an ICT capital deepening positively affects the production function of both sectors through a spillover effect. This positive diffusion effect is intrinsically related to the nature of ICT capital, that is, improving the quality and the speed of communication among economic agents. However, this quality and speed strongly depends on how many economic agents own this technologies. As a simple example, owning a mobile phone enables to contact someone instantaneously if the person you want to reach is endowed by the same technology. As a result, the effectiveness of ICT capital is intrinsically related to its own diffusion. We rationalize this simple line of thought augmenting the production function of each sector in the economy with a spillover effect driven by the diffusion of ICT capital.

Allora ecco perche ICT cresce TFP with some lags...

Matching parameters and results

>>>>

In order to formally explain which mechanism links current ICT to future TFP, we analyze a 2-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy. Both sectoral production functions are fed with three inputs: (i) labor, supplied by households, (ii) hard capital, produced by the final sector, and (iii) ICT capital, produced by the ICT sector. Along with \cite{basu2007information}, we interpret the nature of ICT as a GPT in a neoclassical essence since we assume that exogenous technological changes in the ICT sector are able to affect economy-wide productivity. In particular, when an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy. This ICT capital deepening consequently enhances the productivity of both sectors by means of a spillover. Since the purpose of ICT capital is to improve information sharing, the quality and speed of communication must mainly depend on the diffusion of these technologies among agents. As a simple example, owning a mobile phone enables to contact someone instantaneously if the person you want to reach is endowed with the same technology. As a result, the effectiveness of ICT capital is intrinsically related to its own diffusion. We rationalize this line of thought augmenting the production function of each sector with a spillover effect driven by the diffusion of ICT capital. Consistently with the related literature and our empirical results, the accumulation of ICT capital is a slow process and the benefits of an ICT technology shock show up in the production functions of ICT-users with lags.

As a last step, we use both our empirical and theoretical results to estimate the key parameters of the model via impulse-response function matching to an ICT technology shock. The key parameters within this set are (i) the effectiveness of the spillover effect on the production functions, and (ii) the standard deviation and (iii) persistence of ICT technology shocks.
